% Resume of Gian Peña

\documentclass[letterpaper,9pt]{article} % Changed font size to 9pt

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-.75in}
\addtolength{\textheight}{1.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-8pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% Custom commands
\providecommand{\myemail}{[REDACTED]}
\providecommand{\myphone}{[REDACTED]}
\providecommand{\mylinkedin}{[REDACTED]}

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Gian Marco Peña} \\ \vspace{1pt}
    \small \faPhone\ \myphone $|$ \faEnvelope\ \myemail $|$
    \faLinkedin\ \mylinkedin
\end{center}

%-----------EDUCATION-----------
\section{Education}
\vspace{5pt}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Florida International University}{August 2023 -- December 2026}
      {B.S. Computer Science}{Miami, FL}
      \resumeItemListStart
        \resumeItem{\textbf{Relevant coursework}: Data Structures, Computer Architecture, Systems Programming, Software Engineering}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\vspace{5pt}
  \resumeSubHeadingListStart
		\resumeSubheading
	{Capital One}{June 2025 -- August 2025}
	{Software Engineering Intern}{Chicago, IL}
	\resumeItemListStart
		\resumeItem{Developed device management feature for one of Capital One's customer-facing mobile applications, enabling \textbf{2000}+ members to view active sessions, selectively sign out of devices, and manage account security across platforms.}
		\resumeItem{Built using \textbf{React Native} for mobile, \textbf{React} for web, \textbf{NestJS} backend, and \textbf{MySQL} database with \textbf{Knex.js} for data interactions.}
		\resumeItem{Wrote comprehensive unit tests using \textbf{Jest} across frontend and backend to ensure feature reliability before production release.}
	\resumeItemListEnd
    \resumeSubheading
      {Capital One}{June 2024 -- August 2024}
      {Software Engineering Intern}{McLean, VA}
      \resumeItemListStart
        \resumeItem{Developed software in the Capital One case management platform \textbf{Ease for Associates} to more efficiently organize the load of cases worked by all teams in order to evenly divide cases between over \textbf{1000} teams.}
        \resumeItem{Used \textbf{AngularJS} and \textbf{NgRx} to develop a seamless user interface by creating a platform for associates to work on cases not necessarily under their team's purview, enabling them to take the initiative on working cases.}
        \resumeItem{Wrote unit tests using \textbf{Jest} to ensure rigor in the feature's functionality, verifying that associates without the necessary privileges could not access the feature before it is available to all associates.}
      \resumeItemListEnd
      
    % \resumeSubheading
    %   {Doral Academy Programming Team}{December 2018 -- June 2023}
    %   {Team Member}{Doral, FL}
    %   \resumeItemListStart
    %     \resumeItem{Competed for Doral Academy's programming team, gaining proficiency in data structures, algorithms, and problem-solving techniques. These techniques were applied under pressure. Languages used at competitions include \textbf{C++}, \textbf{Python3}, \textbf{Java}.}
    %     	\resumeItemListStart
	  %          \resumeItem{\textbf{1st place} UF HSPC 2023 (out of approx. 30 teams)}
    %             \resumeItem{\textbf{1st place} FIU HSPC 2023 (advanced division, out of 6 teams)}
    %             \resumeItem{\textbf{2nd place} UCF 37th annual HSPT (out of 74 teams)}
		% \resumeItemListEnd
    %     \vspace{0.15cm}
    % \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Leadership}
\vspace{5pt}
    \resumeSubHeadingListStart
        \resumeSubheading{Reach Program Manager}{January 2024 -- December 2025}{INIT FIU}{Miami, FL}
        \resumeItemListStart
            \resumeItem{Spearheaded technical interview preparation workshops focused on data structures and algorithms, providing students with guidance to excel in their technical interviews.}
            \resumeItem{Developed comprehensive solutions to technical interview problems in \textbf{C++}, \textbf{Java}, and \textbf{Python3}, ensuring accessibility to the discussion of their solutions for a diverse range of students.}
            \resumeItem{Collaborated with authoritative figures within INIT to organize and facilitate these workshops.}
        \resumeItemListEnd
        \resumeSubheading{High School Programming Competition Technical Lead}{February 2024 -- February 2026}{FIU Programming Team}{Miami, FL}
        \resumeItemListStart
            \resumeItem{Operated jointly with technical co-leads on the coordination and execution of our annual high school programming competition, overseeing aspects from initial planning to post-event evaluation.}
            \resumeItem{Automated the generation of large-scale test data sets using \textbf{Bash} and \textbf{Python3}, creating a robust pipeline to validate problem constraints and emulate the judging process.}
            \resumeItem{Configured the contest environment, including setting up and customizing DOMJudge, and authored a diverse set of problem statements to challenge participants’ skills across multiple domains.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
		  \resumeProjectHeading
          {\textbf{FIUJudge} $|$ Contest Environment $|$ Hybrid}{June 2025 -- Present}
          \resumeItemListStart
            \resumeItem{Developed a full-stack web application using \textbf{React} and \textbf{Express.js} with \textbf{SQLite} database to host high school programming contests for \textbf{30+} teams, replacing the existing judging platform for university-sponsored competitions}
            \resumeItem{Implemented comprehensive contest features including real-time scoreboards, submission judging, clarification systems, contest announcements, and administrative oversight tools}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{BedStats} $|$ Discord Bot $|$ Remote}{June 2020 -- Present}
          \resumeItemListStart
            \resumeItem{Leveraged \textbf{Node.js}, Discord’s API and other \textbf{RESTful API} technologies to create a robust and scalable Discord bot, empowering users to access comprehensive Bedwars data within their own profiles or those of other players from the Hypixel Minecraft server.}
            \resumeItem{Successfully deployed the bot to approximately \textbf{5000} Discord servers, benefiting a diverse user base and fostering engagement within the gaming community.}
          \resumeItemListEnd
      
    \resumeSubHeadingListEnd
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{HappenIn} $|$ Event Discovery Platform $|$ KnightHacks}{October 2025}
          \resumeItemListStart
            \resumeItem{Created a mobile-friendly website inspired by Tinder, enabling users to discover local events and activities, and connect with others who share mutual interests.}
            \resumeItem{Designed the frontend using \textbf{React} for a seamless, responsive user experience.}
            \resumeItem{Engineered a backend split into two services: a \textbf{RESTful API} built with \textbf{Express.js} (Node.js) for core data operations, and a WebSocket server for real-time chat using the \textbf{ws} npm package for activity-based group messaging.}
            \resumeItem{Utilized \textbf{SQLite} to efficiently store and retrieve chat messages, ensuring reliable persistence and fast access for real-time conversations.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
    
\section{Technical Skills}
\vspace{5pt}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, C++, Python3, Java, \LaTeX, Bash, Zsh, SQLite, MySQL} \\
     \textbf{Frameworks}{: Node.js, Express.js, React, React Native, Jest}
    }}
 \end{itemize}

\end{document}
